CommonMind Consortium: DLPFC

### 2020-09-18 combined_analysis/diff.networks.Rmd
Update diff networks

@@

>>>>

```{r sex.confounding}
form = ~ Reported_Gender + GABA + GLU + Olig + MgAs + ageOfDeath 
par(mfrow=c(2,2))
lapply( unique(METADATA$Institution), function(INST){
	i = METADATA$Institution == INST
	C = canCorPairs(form, METADATA[i,]) 
	plotCorrMatrix(C, main=INST)
})
```

@@

# Interaction analysis

## Difference networks
```{r diff.networks.Dx_Sex}

METADATA$Dx_Sex = with(METADATA, paste(Reported_Gender, Dx, sep='_'))
METADATA$Dx_Sex = factor(METADATA$Dx_Sex, c('Female_Control', 'Female_SCZ', 'Male_Control', 'Male_SCZ'))

resVersion = "Dx_Sex"
variable = 'Dx_Sex'

net.Dx_Sex = get_networks(resid.add[[resVersion]], METADATA, variable)

lvls = levels(METADATA$Dx_Sex)

print(paste0('(',lvls[4], ' - ',lvls[3], ') - (',lvls[2], ' - ',lvls[1], ')'))

# Discover clusters in first cohort
#----------------------------------
C = net.Dx_Sex[[1]]
C.diff.discovery = (C[[lvls[4]]] - C[[lvls[3]]]) - (C[[lvls[2]]] - C[[lvls[1]]])

C.diff.discovery = C.diff.discovery[keep.ensID,keep.ensID]

dynamicColors.Dx_Sex = labels2colors(dynamicMods, colorSeq = colors())
tab = table(dynamicColors.Dx_Sex)
hist(tab, xlab="Cluster size")
```

```{r testing.Dx_Sex}
# Hypothesis testing     
df_test.Dx_Sex = test_differential_correlation_interaction(resid.add[[resVersion]], C.diff.discovery, dynamicColors.Dx_Sex, METADATA, nperm=100)  
```

## Discovery cohort
```{r plot.discovery.Dx_Sex}
# plot discovery and testing.  
ggplot(df_test.Dx_Sex, aes(Module, -log10(FDR))) + geom_bar(stat='identity', fill=df_test$Module) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + coord_flip() + facet_wrap(~Cohort) + ylab(bquote(-log[10]~FDR)) + scale_y_continuous(expand=c(0,0)) + geom_hline(yintercept = -log10(0.05), color="red", linetype="dashed")
```

```{r modules.in.discovery.Dx_Sex, fig.width=10, fig.height=50}

	plot_module( mod, df_test.Dx_Sex, METADATA, dynamicColors.Dx_Sex, C.diff.discovery, resid.add[[resVersion]], variable, "MSSM-Penn-Pitt")   
	})

## Replication cohort
```{r second.cohort.Dx_Sex, fig.width=6, fig.height=12}
df_cohort2 = df_test.Dx_Sex[df_test.Dx_Sex$Cohort == "NIMH-HBCC",]
df_cohort2$Module = factor(df_cohort2$Module, unique(df_cohort2$Module))
table(df_cohort2$FDR < 0.05)

```{r modules.in.second.cohort..Dx_Sex, fig.width=8, fig.height=100}

	plot_module( mod, df_test.Dx_Sex, METADATA, dynamicColors.Dx_Sex, C.diff.discovery, resid.add[[resVersion]], variable, "NIMH-HBCC")   
	})
